%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Mohammad Abbasi Resume
% English version — kept in sync with persian.tex
% This document needs to be compiled with XeLaTeX.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper]{deedy-resume}

\begin{document}
\hypersetup{pdfborder = {0 0 0}}

%----------------------------------------------------------------------------------------
% TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated
\namesection{Mohammad}{Abbasi}{
Website: \href{http://zilabs.ir}{\bf http://zilabs.ir} | Phone: +989106091633 \\
\href{mailto:absi1377@hotmail.com}{absi1377@hotmail.com} |
\href{https://www.linkedin.com/in/ma14ch}{Mohammad Abbasi Chahardah Cherik (LinkedIn)} |
GitHub: \href{https://github.com/ma14ch}{ma14ch}
}

\vspace{1em}

%----------------------------------------------------------------------------------------
% FIRST PAGE: EXPERIENCE AND SKILLS
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.62\textwidth}
\small
\textcolor{gray}{\huge{Experience}}
\vspace{\topsep}

\textbf{Faragostar} | AI Engineer \\
\vspace{\itemsep}
Apr 2025 – Present (Hybrid) | Tehran, Iran
\begin{tightitemize}
\item Built a letter-authoring chatbot for Faragostar's correspondence-automation system using n8n.
\item Developed an n8n-based RAG chatbot for intelligent document search.
\item Built a query-optimization system to modernize the legacy search workflow using n8n.
\item Developed an n8n-based automated customer-response system.
\item Developed and optimized Persian RAG systems for document retrieval using LangChain and LangGraph.
\item Implemented, improved, and deployed enterprise-scale OCR, Summarizer, Feature Extraction, and Letter Writer services.
\item Designed and improved Text-to-Speech and Speech-to-Text services through model fine-tuning and prompt optimization.
\item Integrated and deployed language models (Qwen, Aya, Gemma, LLaMA) on Docker, Ollama, and VLLM infrastructure.
\item Designed and implemented AgentCore and Agentic Systems modules with Long-Term Memory and interactive graphs.
\item Managed and optimized infrastructure, including Docker networking, Kong API Gateway, PostgreSQL, and SQL Server.
\item Fine-tuned language and speech models (Mana TTS and ASR) and designed training and evaluation pipelines.
\item Fully documented services, managed Git repositories, and cleaned up codebases and documentation.
\end{tightitemize}
\vspace{\topsep}

\colorbox{black}{\phantom{\fontspec[Path = fonts/lato/]{Lato-Bol}\selectfont\textbf{Malek Ashtar University} | Researcher}} \\
\vspace{\itemsep}
\colorbox{black}{\phantom{\fontspec[Path = fonts/lato/]{Lato-Lig}\selectfont Feb 2025 – Present (Part-time) | Tehran, Iran}} \\
\colorbox{black}{\phantom{\fontspec[Path = fonts/lato/]{Lato-Lig}\selectfont\textbullet\ Satellite image processing (SAR/ISAR).}} \\
\vspace{\topsep}

\textbf{Demis} | AI Specialist \\
\vspace{\itemsep}
Feb 2025 – Apr 2025 | Isfahan, Iran
\begin{tightitemize}
\item Speech-to-text project.
\item AI-powered medical assistant project.
\end{tightitemize}
\vspace{\topsep}

\textbf{Entekhab Industrial Group} | AI Specialist \\
\vspace{\itemsep}
Nov 2023 – Apr 2024 | Isfahan, Iran, SnowaTec
\begin{tightitemize}
\item RAG for instruction manuals.
\item Food recommender system using a Telegram bot (available on GitHub).
\item Feature extraction and named-entity recognition through language-model fine-tuning.
\item Text generation and feature extraction using large language models.
\item Built translation models using Transformers (available on GitHub).
\item Developed a food recommender system based on food ingredients.
\item Used ASR, TTS, large language models, and generative AI with NVIDIA\texttrademark NEMO.
\item Gathered and analyzed user comments about Digikala and Amazon products (available on GitHub).
\item ...
\end{tightitemize}
\vspace{\topsep}

\textbf{Entekhab Industrial Group} | Technology Monitoring Specialist \\
\vspace{\itemsep}
Sep 2022 – Nov 2023 | Isfahan, Iran, SnowaTec
\begin{tightitemize}
\item Monitored the artificial intelligence centers of household-appliance companies (Bosch, Samsung, LG, etc.).
\item Examined the structure of AI platforms and online services of leading home-appliance companies.
\item Conducted patent searches.
\item Benchmarked smart home appliances and future trends.
\item Benchmarked products in the home-appliance sector.
\item Monitored enterprise AI tools.
\item ...
\end{tightitemize}

\end{minipage}
\hfill
\begin{minipage}[t]{0.33\textwidth}
\small

\textcolor{gray}{\huge{Skills}}
\vspace{\itemsep}

\subsection*{AI and LLM Engineering}
Python, FastAPI, Flask, Streamlit \\
LangChain, LangGraph, Hugging Face \\
PyTorch, TensorFlow \\
Qwen, LLaMA, Gemma, Mistral \\
GPT API, Cohere, Sentence Transformers \\

\subsection*{Generative AI and Agents}
RAG, AgentCore, Agentic Systems \\
Long-Term Memory, Prompt Engineering \\
Transformers, Encoder/Decoder \\
n8n \\

\subsection*{Document, NLP and Speech AI}
OCR, Tesseract, OpenCV \\
ASR, TTS, Whisper \\
Summarization, NER, Feature Extraction \\

\subsection*{MLOps and Deployment}
Docker, Docker Compose, Ollama \\
VLLM, NVIDIA\texttrademark NEMO \\
Kong API Gateway, Nginx \\
PostgreSQL, SQL Server \\

\subsection*{Data and Model Training}
Fine-tuning, PEFT, Flash Attention \\
Data Preprocessing, Pandas, NumPy \\
Anaconda \\

\subsection*{Development Tools}
Git, GitHub, VS Code, Postman \\
Gradio, CVAT, Label Studio, LM Studio \\
\LaTeX \\

\subsection*{Additional Skills}
Linux, Windows, R, HTML/CSS \\
Microsoft Office, Photoshop, Canva \\

\end{minipage}

\newpage

%----------------------------------------------------------------------------------------
% SECOND PAGE: EARLIER EXPERIENCE, EDUCATION, AND ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.62\textwidth}
\small

\textbf{Iran Smartech} | Content Creator and Website Designer \\
\vspace{\itemsep}
2021 – 2022 | Isfahan, Iran
\vspace{\itemsep}
\begin{tightitemize}
\item Designed elements and posters with Photoshop.
\item Developed websites using WordPress.
\end{tightitemize}
\vspace{\topsep}

\textbf{Farda Sanjesh Sarmayeh (FSSco.)} | Website Designer \\
\vspace{\itemsep}
2015 – 2016 | Isfahan, Iran
\vspace{\itemsep}
\begin{tightitemize}
\item Developed websites using WordPress.
\end{tightitemize}
\vspace{\topsep}

\textcolor{gray}{\huge{Education}}
\vspace{\topsep}

\textbf{Tarbiat Modares University} | PhD in Artificial Intelligence \\
\vspace{\itemsep}
2025 – Present | Tehran, Iran
\vspace{\itemsep}
\begin{tightitemize}
\item Completed courses in Generative Artificial Intelligence, Complex Networks, Big Data Analytics, Artificial Intelligence Seminar, and Advanced Algorithms.
\end{tightitemize}
\sectionspace

\textbf{University of Isfahan} | MSc in Artificial Intelligence \\
\vspace{\itemsep}
2022 – 2024 | Isfahan, Iran
\vspace{\itemsep}
\begin{tightitemize}
\item Advanced algorithms, advanced theory of computation, advanced artificial intelligence, machine learning, theoretical foundations of cryptography, computational data mining, and deep learning.
\item Healthy food recommender system using users' dietary-habit data mining (thesis).
\item Persian speech-to-speech chatbot (available on GitHub).
\item Big-data recommender system using Two-Tower, DeepFM, and related models.
\item Healthy-food recommender system based on nutritional knowledge.
\item Review of food recommender systems.
\item Big-data preprocessing for deep-learning and machine-learning applications.
\item ...
\end{tightitemize}
\sectionspace

\textbf{University of Isfahan} | BSc in Computer Science \\
\vspace{\itemsep}
2017 – 2022 | Isfahan, Iran
\begin{tightitemize}
\item Computer basics and programming, advanced programming, mathematical foundations, general mathematics 1 and 2, principles of computer systems, combinatorics, matrices and linear algebra, logic and set theory, numerical analysis, operating systems, design and analysis of algorithms, databases, probability, differential equations, linear optimization, theory of computation, algebra, cryptography, coding theory, LaTeX, MATLAB, special topics in computer science (artificial intelligence), and logic circuits.
\end{tightitemize}
\sectionspace

\textcolor{gray}{\huge{Honors and Publications}}
\vspace{\itemsep}
\begin{tightitemize}
\item Graduated in the top 15\% of the BSc cohort — University of Isfahan.
\item Healthy food recommender system via users' dietary-habit data mining — 15th International Conference on Information and Knowledge Technology (IKT).
\end{tightitemize}
\sectionspace

\textcolor{gray}{\huge{Courses Completed}}
\vspace{\itemsep}
\begin{tightitemize}
\item Git — Great Learning (certified).
\item LLM Hackathon — Quera (certified).
\item Data Science Foundations: Data Mining — Lynda.
\item R Programming A–Z: R for Data Science with Real Exercises — Udemy.
\item Learn the 2020 Advanced Python Programming — Udemy.
\item CS50AI 2023 — Harvard University.
\end{tightitemize}
\sectionspace

\textcolor{gray}{\huge{Books Read}}
\vspace{\itemsep}
\begin{tightitemize}
\item Data Mining: Concepts and Techniques (Jiawei Han).
\item Introduction to Algorithms (CLRS).
\item Artificial Intelligence: A Modern Approach (2010, Prentice Hall).
\item Decision Support Systems for Business Intelligence, 2nd edition (2010, Wiley).
\item Matrix Methods in Data Mining and Pattern Recognition (Lars Eldén).
\item Deep Learning with Python (François Chollet).
\end{tightitemize}

\end{minipage}
\hfill
\begin{minipage}[t]{0.33\textwidth}

\textcolor{gray}{\huge{Interests}}
\vspace{\itemsep}

\subsection*{Research Interests}
Large language models \\
Recommender systems \\
SAR and ISAR image processing \\
AI futurology \\
AI policy-making \\
Industry 4.0 \\

\sectionspace
\subsection*{Recent Technology Stack}
\textbf{Languages and Frameworks:} Python (FastAPI, Flask, Streamlit), JavaScript (Node.js), HTML/CSS, Bash Script

\textbf{Infrastructure and Deployment:} Docker, Docker Compose, Docker Swarm, Ollama, VLLM, Llama Factory, Kong API Gateway, n8n, DEC, Nginx, Apache Server, Cloudflare, SQL Server, PostgreSQL, pgAdmin

\textbf{Machine Learning and LLMs:} LangChain, LangGraph, Hugging Face Transformers, PyTorch, TensorFlow, NVIDIA NEMO, Sentence Transformers, Whisper, Qwen, Aya, LLaMA, Gemma, Mistral, GPT API, Cohere

\textbf{Image and Text Processing:} OpenCV, Tesseract OCR, OCR Pipelines, Feature Extraction, Summarizer, Validation Services, Synonym Generator

\textbf{Data Management and Model Training:} Fine-tuning Pipelines, PEFT, Flash Attention, Data Preprocessing (ASR, OCR, TTS), Anaconda, Pandas, NumPy

\textbf{Version Control and Documentation:} Git, GitHub, Markdown, LaTeX, structure.md, README Optimization

\textbf{Development and Testing Tools:} VS Code, Postman, API Explorer, Gradio, Flake8, LM Studio

\sectionspace
\subsection*{Text Models Used}
Qwen 2.5 \\
Qwen 3 \\
Cohere Aya \\
Llama 3 \\
MT5 \\
Sentence-transformer base models \\

\sectionspace
\subsection*{Text + Image Models Used}
Qwen 2.5 VL \\
Mistral \\

\sectionspace
\subsection*{Hobbies}
Photography \\
Cycling \\
Running \\
Theater \\
Cinema \\

\sectionspace
\subsection*{Languages}
Persian (native) \\
English (fluent) \\

\end{minipage}

\end{document}
